Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-02-08 SIR_manuscript.tex
Resolved todo{Fady} comments

\ali{ not sure if we want these 2 following parageraphs, or shrink it into afew short sentences?}
In addition to the favorable-delay-reporting observation of our model \eqref{model}, the model enables us to quantify the amount of delay required in the test reporting process as a strategy to reduce $\Rnum$.
To give a biological interpretation, we describe the qualitative trends predicted by the inequality \eqref{eq:necsuf} \todo{Fady please confirm}. To summarise, returning test results more rapidly tends to be more favorable, i.e., reduces $\Rnum$, when (i) \emph{Confirmed-positive} individuals, lower their contact much more than individuals who are waiting for their test results (i.e., $\eta_c \ll \eta_w$), (ii) the test is highly sensitive, i.e., $p_I$ is close to 1, and (iii) the targeted testing strategy is practiced.

@@

\todo{Fady, can you clean this up}
\begin{align}\label{eq:necsuf}
    &\omega > \omega_2 \nonumber \\
    &\omega > \frac{\gamma}{\sqrt{1-Q}-1} \nonumber \\
    &\vdots \nonumber \\ 
    &\frac{1-n_{t}}{1-n_{w}}P_{i}>\frac{W_{s}}{W_{i}}\left(\frac{\gamma}{\omega}+1\right)^{2}
\end{align}

>>>>

\ali{ not sure if we want these 2 following parageraphs, or shrink it into afew short sentences?}
In addition to the favorable-delay-reporting observation of our model \eqref{model}, the model enables us to quantify the amount of delay required in the test reporting process as a strategy to reduce $\Rnum$.
To give a biological interpretation, we describe the qualitative trends predicted by the inequality \eqref{eq:necsuf} \todo{Fady please confirm}\fady{yes, looks good to me}. To summarise, returning test results more rapidly tends to be favourable (i.e., reduces $\Rnum$) when (i) \emph{Confirmed-positive} individuals, lower their contact much more than individuals who are waiting for their test results (i.e., $\eta_c \ll \eta_w$), (ii) the test is highly sensitive (i.e., $p_I$ is close to 1), and (iii) the targeted testing strategy is used (i.e., $W_i \gg W_s$).

@@

\todo{Fady, can you clean this up}\fady{Done (I think)}
\begin{align}
    &\omega > \omega_2 \nonumber \\
    &\omega > \frac{\gamma}{\sqrt{1-Q}-1} \nonumber \\
    &\sqrt{1-Q} > \frac{\gamma}{\omega}+1 \\
    &1-Q > (\frac{\gamma}{\omega}+1)^2 \\
\end{align}

Substituting in $Q$ from \eqref{eq:defQ} we have

\begin{align}
    &1-\frac{W_i}{W_s}\left(1-\frac{n_{t}-1}{n_{\omega}-1}P_{i}\right)> \left(\frac{\gamma}{\omega}+1\right)^2 \\
    &-\frac{W_i}{W_s}\left(1-\frac{n_{t}-1}{n_{\omega}-1}P_{i}\right)> \left(\frac{\gamma}{\omega}+1\right)^2+1 \\    
    &\frac{W_i}{W_s}\left(\frac{1-n_{t}}{1-n_{\omega}}P_{i}-1\right)> \left(\frac{\gamma}{\omega}+1\right)^2+1\label{eq:necsuf}.
\end{align}

Since all steps in deriving \eqref{eq:necsuf} are reversible, \eqref{eq:necsuf} gives a necessary and sufficient condition for $\omega > \omega_2$, which characterizes when returning tests more rapidly would cause a decrease in $\Rnum$.
